---
title: "VIC RMarkdown Template"
subtitle: "An optional longer subtitle describing the contents of the document."
author:
  - name: Logan Wu^[Department of Health, logan.wu@health.vic.gov.au]
date: "dd/mm/yyyy"
output:
  html_document:
    template: vicdh/vicdh.html
    css: vicdh/vicdh.css
    code_folding: show
    toc: yes
    toc_float:
      collapsed: no
    fig_width: 8.64
toc-title: "On this page"
dh-navbar: yes
resource_files:
- vicdh/fonts/vic/VIC-Regular.woff
- vicdh/fonts/vic/VIC-Bold.woff
- vicdh/fonts/vic/VIC-Medium.woff
- vicdh/fonts/vic/VIC-SemiBold.woff
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```

## Source

The source is available in the [dhhs-crt DevOps](https://dev.azure.com/dhhs-crt/ANALYTICS%20DIME%20ICCOM/_git/R%20Shiny%20Template). If you can't access the repo, ask to be added to the **dhhs-crt** organisation or for someone to export a `.zip` archive.

### Resources

This is a modified version of the default template that uses the Vic font, logo, and navbar.

Place the required files in the same directory as your `.Rmd` document:

- `vicdh.html`
- `vicdh.css`
- `DH Logo White.svg`
- `fonts/*`

### Options

Specify these options in the header YAML. Include the fonts to supply external font files to the user.

```{yaml}
output:
  html_document:
    template: vicdh.html
    css: vicdh.css
resource_files:
- vicdh/fonts/vic/VIC-Regular.woff
- vicdh/fonts/vic/VIC-Bold.woff
- vicdh/fonts/vic/VIC-Medium.woff
- vicdh/fonts/vic/VIC-SemiBold.woff
```


#### Other

Other options available in the default RMarkdown template still work, such as:

```{yaml}
title: "VIC RMarkdown Template"
subtitle: "An optional longer subtitle describing the contents of the document."
author:
  - name: "Namey McHeader"
    affiliation: "Department of Health"
    email: firstname.lastname@health.vic.gov.au
  - name: Namey McFootnote^[Department of Health, firstname.lastname@health.vic.gov.au]
date: "dd/mm/yyyy"
output:
  html_document:
    template: vicdh.html
    css: vicdh.css
    code_folding: show
    toc: yes
    toc_float:
      collapsed: no
    fig_width: 8.64
toc-title: "On this page"
```

## Extra styling {.tabset .tabset-pills}

The template contains some extra styling for Leaflet and DataTable (DT styling also apply to some other tables).

### Leaflet

```{r}
library(leaflet)
leaflet(width = "100%",
        options=leafletOptions(zoomControl=F)) %>%
  addProviderTiles(providers$CartoDB.Positron) %>%
  addMarkers(lng=174.768, lat=-36.852, popup="The birthplace of R", group="Markers") %>%
  addLayersControl(overlayGroups = "Markers",
                       position = "topleft",
                       options = list(collapsed=F))
```

### DataTable

```{r}
library(DT)
datatable(mtcars, style="bootstrap",
          options = list(scrollX = "auto"))
```

### GGPlot

```{r}
library(ggplot2)
ggplot(mtcars, aes(x=mpg, y=cyl)) +
  geom_point()
```

## Contact

Contact the Analytics team / Logan Wu (logan.wu@health.vic.gov.au) with any questions.